---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# tsmvrextras

__tsmvrextras__ is the companion R package to the [tsmvr](https://github.com/spcorum/tsmvr) (Truly Sparse Multivariate Regression) package. __tsmvrextras__ adds functionality by allowing the user to create synthetic datasets or load real datasets that are readily inputted into the *tsmvr* algorithm. It also contains functions to visualize and evaluate the quality of the solutions found by *tsmvr*.

## Installation

You can install the development version of tsmvrextras from [github](https://github.com) with:

``` r
library(devtools)
install_github("tsmvrextras")
```

## Examples

Create a synthetic dataset and use *tsmvr* to perform sparse multivariate regression.

```{r cars}
summary(cars)
```

Evaluate the quality of the solution.

```{r}
summary(cars)
```

Visualize the iterates converging on the solution.

```{r pressure, echo = FALSE}
plot(pressure)
```

Load a real dataset and use *tsmvr* to perform sparse multivariate regression.

```{r}
summary(cars)
```

Alternatively perform k-fold cross-validation using *tsmvr* on the same dataset.

```{r}
summary(cars)
```


## Build and test coverage reports

[![Travis build status](https://travis-ci.org/spcorum/tsmvrextras.svg?branch=master)](https://travis-ci.org/spcorum/tsmvrextras)

[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/spcorum/tsmvrextras?branch=master&svg=true)](https://ci.appveyor.com/project/spcorum/tsmvrextras)

[![Coverage status](https://codecov.io/gh/spcorum/tsmvrextras/branch/master/graph/badge.svg)](https://codecov.io/github/spcorum/tsmvrextras?branch=master)
