---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# tsmvrdata

__tsmvrdata__ is the companion R package to the [tsmvr](https://github.com/spcorum/tsmvr) (Truly Sparse Multivariate Regression) package. __tsmvrdata__ adds functionality by allowing the user to create synthetic datasets or load real datasets that are readily inputted into the *tsmvr* algorithm. It also contains functions to visualize and evaluate the quality of the solutions found by *tsmvr*.

## Development Status

[![Travis build status](https://travis-ci.org/spcorum/tsmvrdata.svg?branch=master)](https://travis-ci.org/spcorum/tsmvrdata)    [![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/spcorum/tsmvrdata?branch=master&svg=true)](https://ci.appveyor.com/project/spcorum/tsmvrdata)    [![Coverage status](https://codecov.io/gh/spcorum/tsmvrdata/branch/master/graph/badge.svg)](https://codecov.io/github/spcorum/tsmvrdata?branch=master)


## Installation

You can install the development version of tsmvrdata from [Github](https://github.com) with:

``` r
library(devtools)
install_github("tsmvrdata")
```

## Examples

Create a synthetic dataset and use *tsmvr* to perform sparse multivariate regression.

```{r cars}
summary(cars)
```

Evaluate the quality of the solution.

```{r}
summary(cars)
```

Visualize the iterates converging on the solution.

```{r pressure, echo = FALSE}
plot(pressure)
```

Load a real dataset and use *tsmvr* to perform sparse multivariate regression.

```{r}
summary(cars)
```

Alternatively perform k-fold cross-validation using *tsmvr* on the same dataset.

```{r}
summary(cars)
```


