---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# Introduction

[tsmvrdata](https://github.com/spcorum/tsmvrdata) is the companion R package to the [tsmvr](https://github.com/spcorum/tsmvr) (Truly Sparse Multivariate Regression) package. [tsmvrdata](https://github.com/spcorum/tsmvrdata) contains cleaned and normalized datasets for use with multivariate (multiple response) regression, and [tsmvr](https://github.com/spcorum/tsmvr) in particualte.

## Development Status

[![Travis build status](https://travis-ci.org/spcorum/tsmvrdata.svg?branch=master)](https://travis-ci.org/spcorum/tsmvrdata)    [![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/spcorum/tsmvrdata?branch=master&svg=true)](https://ci.appveyor.com/project/spcorum/tsmvrdata)    [![Coverage status](https://codecov.io/gh/spcorum/tsmvrdata/branch/master/graph/badge.svg)](https://codecov.io/github/spcorum/tsmvrdata?branch=master)


## Installation

You can install the development version of tsmvrdata from [Github](https://github.com) with:

``` r
library(devtools)
install_github("tsmvrdata")
```

## Loading data

Here is an example of how to load a dataset

```{r concrete}
data(concrete)
```

## Documentation

To see the documentation for a dataset, see its corresponding help page.

## Datasets

Here is a list of the datasets included in this package:

* concrete - concrete measurement and quality attributes
* facebook - facebook page attributes and user responses
* location - mobile device locations
* propolsion - simulated naval engine propulsion measurements
* stocks - stock performace
* dataset 6 - my description
* dataset 7 - my description
* dataset 8 - my description
* dataset 9 - my description
* dataset 10 - my description


